Generative Models for scRNA

### 2018-03-21 generativemodelsforscrna/outline.tex
clarified aggregate posterior plots marginally

Scatterplot of the aggregate posterior distribution of $Z_{T_0}$, colored by posterior mean of the cluster assigment:

@@

Notice that there are only so many clusters that are really clearly distinct in this latent space.  However, let's focus on that cluster on the right-hand side.  What happens if we look at the $Z_{T_1}$ variables for those cells?  We get substantial subclustering apparent in the $Z_{T_2}$ space:

>>>>

Scatterplot of the aggregate posterior distribution of $Z_{T_0}$, colored by posterior mean of the cluster assigment.  That is, each dot is a cell, its position is given by a posterior sample of $Z_{T_0}$, and its color has something to do with what cluster we expect it to be in.

@@

Notice that there are only so many clusters that are really clearly distinct in this latent space.  However, let's focus on that cluster on the right-hand side.  What happens if we look at the $Z_{T_1}$ variables for those cells?  We get substantial subclustering apparent in the $Z_{T_1}$ space.  In the following picture, each dot is a cell from the cluster on the right-hand-side of the previous figure, and the position is given by a posterior sample of $Z_{T_1}$.
